Interactive Curvature Tensor Visualization on Digital Surfaces\thanks{This work has been mainly funded by \textsc{DigitalSnow} ANR-11-BS02-009, \textsc{KIDICO} ANR-2010-BLAN-0205 and \textsc{PRIMES Labex} ANR-11-LABX-0063/ ANR-11-IDEX-0007 research grants.}

### 2015-10-23 latex/article.tex
minor edit

For all illustrations, we use directly normal vectors computed by algorithm
discussed in Section~\ref{sec:curv-tens-estim}

@@

  \end{center}
  \caption{Comparison of number of texture fetches, $L_2$ and $L_\infty$ error obtained on OctaFlower with a digital domain of $130^3$. We measured it using radii of 8 and 16.
  The object was triangulated at full resolution with a regular grid and contains 282396 vertices. The timings
    only consider the curvature estimation step.\label{tab:full-res-stat}}
\end{table}

@@

We can first note that the required time for an object to compute ground truth
curvature is usually as high as the time required to extract the geometry and
compute all the above levels. Using approximations is thus mandatory, since for
big objects such as the XYZ-Dragon ($510^3$) with big radii the approximate
computation is faster than the $l_0$ while results are enough close to the
$l_0$. For example, with $R=20$, the approximated visualization at $l_2$ takes
only $300$ms while the $l_0$ visualization takes more than $4$ seconds.

We can thus get an approximated visualisation of our object as soon as we run
the application, allowing for real time interactions with the object (changing
the visualized value, the curvature radius, \cdots). It is also clear on those
graphs that using a hierarchical decomposition reduces the curvature computation
time. For the XYZ-Dragon with $R=20$, it needs almost $4$ seconds to compute the
$l_0$ level, whereas using the hierarchical algorithm, it only needs $700$ms.
However, due to the precomputation, this algorithm is biased and creates an
error (presented in Table~\ref{tab:full-res-stat}) that needs to be considered.

@@

>>>>

@@

  \end{center}
  \caption{Comparison of number of texture fetches, $L_2$ and $L_\infty$ error obtained on OctaFlower with a digital domain of $130^3$. We measured it using radii of 8 and 16.
  The object was triangulated at full resolution with a regular grid and contains 282,396 vertices. The timings
    only consider the curvature estimation step.\label{tab:full-res-stat}}
\end{table}

@@

We can first note that the required time for an object to compute ground truth
curvature is usually as high as the time required to extract the geometry and
compute all the above levels. Using approximations is thus mandatory, since for
big objects such as the XYZ-Dragon ($510^3$) with big radii the approximate
computation is faster than the $l_0$ while results are enough close to the
$l_0$. For example, with $R=20$, the approximated visualization at $l_2$ takes
only 300ms while the $l_0$ visualization takes more than 4 seconds.

We can thus get an approximated visualisation of our object as soon as we run
the application, allowing for real time interactions with the object (changing
the visualized value, curvature radius, \cdots). It is also clear on those
graphs that using a hierarchical decomposition reduces the curvature computation
time. For the XYZ-Dragon with $R=20$, it needs almost 4 seconds to compute the
$l_0$ level, whereas using the hierarchical algorithm, it only needs 700ms.
However, due to the precomputation, this algorithm is biased and creates an
error (presented in Table~\ref{tab:full-res-stat}) that needs to be considered.

@@

Figure~\ref{fig:adaptive} shows curvature computation and exploration in
real-time on large datasets: XYZ-Dragon (with digital domain of $512^3$) and
Snow microstructures ($233^3$).
